Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
added rational section order

\todo{Include one of the following, if the first one, include a 
remark for quotient}
\iffalse{
\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]
\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{rem}
In particular, in the case of
\[
	\begin{tikzcd}
		I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
		\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
		I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
inducing
\[
	I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
\]
\todo{how do we make this proof?}
\end{rem}
}\fi

\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
generated in degree 1 that are equipped with monomial ordering $\prec$.
Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
\[
	\begin{tikzcd}
	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
Further suppose that $I'$ is generated over $I$ by elements $f_1,
\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
is of the form $y_i$. Then, the elements $f_i$ determine minimal
generators for $I'$ over $I$.
\end{lem}

\begin{proof}
Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
\]
\[
	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
\]

\noindent
determines map of rings, no longer necessarily graded. 
By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
\[
	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
\]
so
\[
	\dim_k (I'/I)_2=j.
\]
This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{rem}
\label{rem:minimal_quadratic_trivial_case}
It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
are $k$-minimal generators for $I'$ (over the trivial base vector
space). 
\end{rem}

@@

Before presenting a proof of this, we first prove a lemma that will allow parts $(b)$ and $(c)$ to immediately follow from an appropriate construction of generators in part $(a)$.

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$ and $\halfcan'$ are $\mathbf{Q}$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.  Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.  Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $R_{\halfcan'}$.  Moreover, suppose there is some ordering $\prec$ such that if $f\in S$ and $g\not\in S, g\not\in R_{\halfcan'}$ is a quadratic monomial in $x_1, \ldots, x_m, y_1, \ldots, y_n$ in the same degree as $f$, then $g\prec f$.  Then if $I$ and $I'$ are the ideal of relations of $R_{\halfcan'}$ and $R_{\halfcan}$ with the given generating sets, then 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
Furthermore, if $T$ consists only of quadratic monomials, then $I$ is minimally generated over $I'$ by a Grobner Basis with an initial term for each element of $T$.
\end{lem}
\begin{proof}

\end{proof}

\begin{proof}[Proof of Lemma \ref{lem:deg1-sat-ind}]
By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
by construction, so any product of $\prod z_i$ of elements of
degrees less than $d_i$ must have 
\[
	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
\]

@@

Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.  Choose an element of the form $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ as described in the previous paragraph, in degree with $d_l= 1$ and if 
$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
\[
	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
\]

@@

\begin{defn}
\label{defn:admissible}
Let $(\sx', 0, L'),(\sx, 0, L)$ be log spin
curves, both ramified over ramified at $Q_1, \ldots, Q_r$. Suppose
there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where

@@

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number. What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
\begin{enumerate}
	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}$.
	\item[(Ad-ii)] Either $e_j' = 3$ for all $j \in \{1, \ldots, r\}$
		or any generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] The minimality condition
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

\begin{lem}\label{lem:n-3s-admissible}
Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$. Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$. Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
\end{lem}
\begin{proof}
To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$). Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i). Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}= 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}

@@

\begin{thm}
\label{thm:ram_order_ind}
Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and
$(\sx', J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' =
R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}. Let
$(\sx, \Delta, \halfcan)$ be another log spin curve
with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
$e_j = e_j'$ for $j \notin J$. Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i, e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-ord_{Q_i}(y_{i, e_i}) = \frac{e_i - 1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
\subhalf{
			e_j'} - \frac{1}{\deg(y_{i, e_i})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i, e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y, x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
			\neq y_{i, e_i}, y_{i, e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e
		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
		minimal generators for $I'$ together with any set of relations 
as in 
		part (c) minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

\begin{proof}
Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log spin curves in 
question, with coarse spaces $X = X'$. 
\todo{possibly generalize these to arbitrary log  $\Delta \neq 0$ spin curves}
Define

@@

\section{Further Research}
\label{sec:further-questions}
\begin{itemize}
	\item More on fractional modular forms
	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_11} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})? \todo{Possibly think more about this} 
	\item Generic Initial ideal (and other genericness properties?)
	\item Complete minimal generation
\end{itemize}

>>>>

\todo{Include one of the following, if the first one, include a 
remark for quotient}
\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1, \ldots, x_n] \rightarrow B$ be a map of graded
rings with kernel $I,$ such that $I$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]
\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{rem}
In particular, in the case of
\[
	\begin{tikzcd}
		I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
		\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
		I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
inducing
\[
	I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
\]
\todo{how do we make this proof?}
\end{rem}

%
%\begin{lem}
%\label{lem:minimal_quadratic_2}
%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
%generated in degree 1 that are equipped with monomial ordering $\prec$.
 %Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
%\[
	%\begin{tikzcd}
	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	%\end{tikzcd}
%\]
%Further suppose that $I'$ is generated over $I$ by elements $f_1,
%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
%is of the form $y_i$. Then, the elements $f_i$ determine minimal
%generators for $I'$ over $I$.
%\end{lem}
%
%\begin{proof}
%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
%degree 1. Then,
%\[
	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
%\]
%\[
	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
%\]
%
%
%\noindent
%determines map of rings, no longer necessarily graded. 
%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
%\[
	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
%\]
%so
%\[
	%\dim_k (I'/I)_2=j.
%\]
%This implies any set of
%generators for $I$ must have at least $j$ elements. Since $f_1,
%\ldots, f_j$ is such a set, it is minimal.
%\end{proof}
%
%
%\begin{rem}
%\label{rem:minimal_quadratic_trivial_case}
%It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
%case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
%are $k$-minimal generators for $I'$ (over the trivial base vector
%space). 
%\end{rem}

@@

\begin{proof}
By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
by construction, so any product of $\prod z_i$ of elements of
degrees less than $d_i$ must have
\todo{Aaron: at what point is the following order taken at?}
\[
	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
\]

@@

Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
corresponds to the best lower approximation $\frac{c_j}{d_j}$. Recall from the previous 
paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l= 1$ and if 
$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
\[
	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
\]

@@

\begin{defn}
\label{}
If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
\end{defn}

\begin{defn}
\label{defn:admissible}
Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
curves, both ramified over ramified at $Q_1, \ldots, Q_r$. Suppose
there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where

@@

\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number. What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
\begin{enumerate}
	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-\ord_{Q_i}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}$.
	\item[(Ad-ii)] If every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
		\begin{align*}
			\frac{-\ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] The minimality condition
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

\begin{lem}\label{lem:n-3s-admissible}
Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$. Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$. Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
\end{lem}
\begin{proof}
To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$). Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i). Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}

@@

\begin{thm}
\label{thm:ram_order_ind}
Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and either $e_1' = \cdots = e_r' = 3$ or $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' =
R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}. Let
$(\sx, \Delta, \halfcan)$ be another log spin curve
with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
$e_j = e_j'$ for $j \notin J$. Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i, e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-\ord_{Q_i}(y_{i, e_i}) = \frac{e_i - 1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
\subhalf{
			e_j'} - \frac{1}{\deg(y_{i, e_i})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i, e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y, x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
			\neq y_{i, e_i}, y_{i, e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e
		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
		minimal generators for $I'$ together with any set of relations 
as in 
		part (c) minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

\begin{proof}
We will only prove this in the harder case $(\sx, L', J)$ is admissible, as the case $e_1 = \cdots = e_r = 3$ is similar.

Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log spin curves in 
question, with coarse spaces $X = X'$. 
\todo{possibly generalize these to arbitrary log  $\Delta \neq 0$ spin curves}
Define

@@

\section{Further Research}
\label{sec:further-questions}
\begin{itemize}
	\item More on fractional modular forms
	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_11} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})? \todo{Possibly think more about this} 
	\item Generic Initial ideal (and other genericness properties?)
\end{itemize}
